Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-14 trunk/lids/twittersearchwrap/paper/paper.tex
removed commented out parts in abstract

\begin{abstract}
Microblog messages contain so-called hashtags which are usedto mark keywords or topics. To facilitate understanding the meaning of a hashtag in the context of microblog, we have developed a system which annotates hashtags based on Twitter search results with encyclopedia entities that best describe the hashtag, thus offering means of quickly grasping the meaning of the hashtag and relating the hashtags to external content, thus providing starting points for further exploration of the hashtags' context. In an evaluation we analyse the stability of the related entities.
\end{abstract}

Keywords: Twitter, Wikipedia, DBpedia, RDF

\nop{
http://tagdef.com/ has a list of popular tags
}

@@

Microblogging has become more and more popular over the last years, especially with the most prominent and most widely used microblogging platform Twitter\footnote{\url{http://twitter.com}} which has become very influential. The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of Twitter the restriction is 140 characters. Twitter has a total of about 190 million of users who produce 65 million Twitter messages a day. Thus, Twitter represents a huge data source on the web.

On microblogging platforms it is possible to search for messages containing a specific hashtag. This search returns the most recent messages containing the tag. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used. To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds. These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.

Furthermore, this annotation will help to understand hashtags. Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms. For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$. If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform. However, understanding a search result is difficult and time-consuming. Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result. These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean. If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag. A system may be envisioned which automatically finds entitities which are equivalent to a hashtag. Thus, these hashtag-entity pairs may be used similarly to systems in which hashtags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.

Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message. Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used. For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe. The tag $\#ka$ is however also used in the context of the car type Ford Ka. Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka. An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.

In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities. While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}. Thus, we chose to generate annotations for the whole search result.

Our implementation is based on Twitter, the most widely used and biggest microblogging platform, and on Wikipedia. The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}). External data sources also map to DBpedia, thus combined querying of external sources and Twitter search results becomes possible. Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g. there is no entity in DBpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not be mapped directly.

Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change. In an evaluation of our approach we have tried to analyse the stability of the result.

Our contributions thus are:
\begin{itemize}
	\item We present an approach for finding entities which are related to search results on microblogging platforms
	\item We specify a formatting of microblogging messages as RDF
	\item We evaluate the stability of the found entities.
\end{itemize}

The remainder of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.

@@

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l}
Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
$\#tilltheworldends$ & false & Britney Spears & .9583 \\
& &  iTunes & .6875 \\
& &  itunes & .625 \\ 
\hline
$\#nowplaying$ & false & iTunes & .5208 \\
& & Michael Jackson & .333 \\
& & Lady Gaga & .333 \\
\hline
$\#nowplaying$ & true & YouTube & .8235 \\
& & Hip Hop Music & .6471 \\
& & The Notorious B.I.G. & .5883 \\
\hline
$\#np$ & false & Chris Brown\_(entertainer) & .5 \\
& & Usher & .3125 \\
& & Lil Wayne & .2917 \\
\hline
$\#np$ & true & Chris Brown\_(entertainer) & .5 \\
& & YouTube & .375 \\
& & Ne-Yo & .315 \\
\hline
$\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
& & Twitter & .2291 \\
& & twitter & .1667 \\
\hline
$\#thataintwinning$ & true & twitter & .5208 \\
& & Twitter & .5 \\
& & Two and a half men & .125 \\
\hline
$\#blackpeoplemovies$ & false & Devil & .4791 \\
& & Tyler Perry & .2708 \\
& & Harry Potter & .2292 \\
\hline
$\#blackpeoplemovies$ & true & Amazon.com & 1 \\
& & YouTube & 1 \\
& & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}

>>>>

\begin{abstract}
Microblog posts may contain so-called hashtags that mark keywords or topics.
Hashtags are used in an ad-hoc fashion; the meaning of hashtags is implicitly defined via their use, which makes understanding and querying hashtags difficult.
In this paper we devise a method for annotating microblog posts which contain hashtags with related encyclopedia entities.
Thus, users have the means to quickly grasp the meaning of a hashtag, and gain starting points for further exploration of the hashtags' context.
We implement two variants of our method based on an existing system for linking content to Wikipedia and analyse the stability of annotated  Twitter search results for popular hashtags.
\end{abstract}

\nop{
Keywords: Twitter, Wikipedia, DBpedia, RDF

http://tagdef.com/ has a list of popular tags
}

@@

Microblogging services allow users to publish short messages online.
Twitter\footnote{\url{http://twitter.com/}} is the largest dedicated microblogging site; as of March 2011, its users create an average of 140 millions post a day\footnote{\url{http://blog.twitter.com/2011/03/numbers.html}}.
Given a 140-character limit for posts, Twitter users invented shortcuts for certain expressions.
So-called hashtags (starting with a \# sign followed by a keyword) are frequently used to associate posts with a specific topic, place, person or event.
For example, posts covering current events in Lybia are frequently tagged with $\#Libya$.
%the Extended Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.

Hashtags can help to organise microblog messages and thus are useful for supporting search.
Microblogging platforms offer functionality to search for messages containing a specific hashtag.
%This search returns the most recent messages containing the tag.
However, as hashtags are implicitly defined via their use, the meaning of a hashtag is often unclear.
Services such as tagdef\footnote{\url{http://www.tagdef.com/}} provide means to provide a definition of a hashtag, but these services rely on user input and thus only cover a subset of all hashtags.
In addition, since hashtags are not related to other structured information sources, querying is limited to direct keyword search.

We propose a method to associate hashtags to encyclopedia entities.
In our experiments we use Wikipedia as entity source which covers a wide range of topics.
Furthermore, automatic tools for annotating text with Wikipedia entities are readily available, for example Milne and Witten's Wikifier \cite{key:wikifier}.
Wikipedia entities are widely linked to external data sources via DBpedia \cite{key:dbpedia}, thus combined querying of DBpedia and Twitter becomes possible.

Matching entities in microposts is a difficult problem \cite{key:clef} as microblog post are very short and contain little information.
Our approach uses search results for a given hashtag as input to the entity matching component and returns messages using the hashtag including a set of related Wikipedia entities.
% which have been detected in the search result.
The matched entities not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
%These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean.

%with a set of entities which reflect the content of the result feeds.
%, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
%grasp the context of the results and to get further information on the topic that was searched for.
%To facilitate this putting into context of the search results, 
%Furthermore, this annotation will help to understand hashtags. 
%If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform.
%However, understanding a search result is difficult and time-consuming.

\nop{
Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message.
}

In this paper, we present a method to automatically annotate hashtag search results with encyclopedia entities.
If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag.
We envision a system which automatically finds entities equivalent to a hashtag.
%While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
%Thus, we chose to generate annotations for the whole search result. 
%Our implementation is based on Twitter, the most widely used and biggest microblogging platform, and on Wikipedia.
Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change.
In an evaluation of our approach we analyse the stability of the results of the entity matching for hashtag search results.

Our contributions thus are:
\begin{itemize}
	\item We present an approach for finding entities which are related to search results on microblogging platforms.
%	\item We specify a formatting of microblogging messages as RDF.
	\item We evaluate the stability of the found entities.
\end{itemize}

The remainder of this paper is organised as follows: Section~\ref{sect:method} overviews the approach,
Section~\ref{sect:impl} presents the implementation,
Section~\ref{sect:eval} covers the results of the evaluation,
Section~\ref{sect:relWork} discusses related work and  Section~\ref{sect:conclusion} concludes.

@@

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l|l}
Hashtag & Definition on tagdef.com & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
\#tilltheworldends & - & false & Britney Spears & .9583 \\
& & &  iTunes & .6875 \\
& & &  itunes & .625 \\ 
\hline
\#nowplaying & What people on Twitter & false & iTunes & .5208 \\
             & are currently listening & & Michael Jackson & .333 \\
             & to. & & Lady Gaga & .333 \\
\hline
\#nowplaying & same & true & YouTube & .8235 \\
             &  &  & Hip Hop Music & .6471 \\
             &  &  & The Notorious B.I.G. & .5883 \\
\hline
\#np         & Now playing = \#NP & false & Chris Brown\_(entertainer) & .5 \\
& & & Usher & .3125 \\
& & & Lil Wayne & .2917 \\
\hline
\#np & same & true & Chris Brown\_(entertainer) & .5 \\
& & & YouTube & .375 \\
& & & Ne-Yo & .315 \\
\hline
\#thataintwinning & -& false & Mozilla Firefox & .2291 \\
& & & Twitter & .2291 \\
& & & twitter & .1667 \\
\hline
\#thataintwinning & - & true & twitter & .5208 \\
& & & Twitter & .5 \\
& & & Two and a half men & .125 \\
\hline
\#blackpeoplemovies & - & false & Devil & .4791 \\
& & & Tyler Perry & .2708 \\
& & & Harry Potter & .2292 \\
\hline
\#blackpeoplemovies & - & true & Amazon.com & 1 \\
& & & YouTube & 1 \\
& & & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}
